CMPSubset

### 2021-08-16 CMP/CMPSubset.Rmd
Looking for new Taqman probes; Identifying clustree optimal resolution

```{r setup}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
# library(clustree)
```

@@

store session info
```{r }
# sink("CMP-v1.20210616.txt")
sessionInfo()
# sink()
```

```{r}
source("msAggr_AnalysisCode/read_10XGenomics_data.R")
source("msAggr_AnalysisCode/PercentVariance.R")
source("msAggr_AnalysisCode/Mouse2Human_idconversion.R")
```

```{r}
setwd("../cellRanger/") # temporarily changing wd only works if you run the entire chunk at once
data_file.list <- read_10XGenomics_data(sample.list = "CMPm2")
object.data <-Read10X(data_file.list)
```

@@

```{r}
plot1 <- FeatureScatter(cmp.object, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "orig.ident", pt.size = 0.01)
plot2 <- FeatureScatter(cmp.object, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "orig.ident", pt.size = 0.01)
plot1 + plot2
```

We don't have to worry about comparing library depths, so we'll just do normalization/Scale data

remove low quality cells
require: nFeature_RNA between 200 and 4000 (inclusive)
require: percent.mt <=5

@@

Find variable features
```{r fig.width = 5, fig.height = 2}
cmp.object <- FindVariableFeatures(cmp.object, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(cmp.object), 10)
plot1 <- VariableFeaturePlot(cmp.object)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2

Scale data (linear transformation)

@@

```{r}
clust3.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster3cellIDs.txt", col.names = "clust03")
clust3.cells <- sapply(clust3.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust17.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster17cellIDs.txt", col.names = "clust17")
clust17.cells <- sapply(clust17.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust10.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster10cellIDs.txt", col.names = "clust10")
clust10.cells <- sapply(clust10.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust11.cells <- read.table(file = "Seuratv1_clusterCellIDs/cluster11cellIDs.txt", col.names = "clust11")
clust11.cells <- sapply(clust11.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
```

@@

@@

@@

Create `FindAllMarkers()` lists for GSEA
```{r}
Idents(cmp.object) <- "RNA_snn_res.2.5"
res.2.5.allmarkers <- FindAllMarkers(cmp.object)
```

Map HGNC symbols
```{r}
Mouse2HumanTable <- Mouse2Human(res.2.5.allmarkers$gene)

@@

calculate `FindMarkers()` that distinguish each cluster (might overlab between clusters)
```{r}
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1", "RNA_snn_res.1.5", "RNA_snn_res.2", "RNA_snn_res.2.5", "clust.ID")
for(tested.ident in ident.list){
	for (cluster in sort(as.numeric(levels(cmp.object@meta.data[[tested.ident]])))){
	cluster.markers <- FindMarkers(cmp.object, ident.1 = cluster)
	xlsx::write.xlsx(x = cluster.markers[,c("avg_log2FC", "p_val_adj")], 
									 file = paste0(projectName, "_FindMarkers_", gsub("RNA_snn_", "", tested.ident), ".xlsx"), 
									 sheetName = paste0("clst", cluster), 
									 col.names = TRUE, 
									 row.names = TRUE, 
									 append = TRUE)
}
}
```

@@

# Cell cycle analysis
Just so we know what we're working with

```{r}
s.genes <- cc.genes.updated.2019$s.genes
g2m.genes <- cc.genes.updated.2019$g2m.genes
```

# Compare @ hierarchcial clusteirng

>>>>

```{r setup}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(clustree)
```

@@

store session info
```{r}
sessionInfo.filename <- paste0(projectName, "_sessionInfo.txt")
sink(sessionInfo.filename)
sessionInfo()
sink()
```

```{r}
source("../RFunctions/read_10XGenomics_data.R")
source("../RFunctions/PercentVariance.R")
source("../RFunctions/Mouse2Human_idconversion.R")
```

```{r warning=FALSE}
setwd("../../cellRanger/") # temporarily changing wd only works if you run the entire chunk at once
data_file.list <- read_10XGenomics_data(sample.list = "CMPm2")
object.data <-Read10X(data_file.list)
```

@@

```{r}
plot1 <- FeatureScatter(cmp.object, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "orig.ident", pt.size = 0.01)
plot2 <- FeatureScatter(cmp.object, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "orig.ident", pt.size = 0.01)
plot1 + plot2
```
## Filter data
remove low quality cells
require: nFeature_RNA between 200 and 4000 (inclusive)
require: percent.mt <=5

@@

Find variable features
```{r fig.width = 5, fig.height = 2}
cmp.object <- FindVariableFeatures(cmp.object, selection.method = "vst", nfeatures = 2000)
top10 <- head(VariableFeatures(cmp.object), 10)
plot1 <- VariableFeaturePlot(cmp.object)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2
```

## Scale data (linear transformation)
We don't have to worry about comparing library depths, so we'll just do normalization/Scale data

@@

```{r}
clust3.cells <- read.table(file = "../Seuratv1_clusterCellIDs/cluster3cellIDs.txt", col.names = "clust03")
clust3.cells <- sapply(clust3.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust17.cells <- read.table(file = "../Seuratv1_clusterCellIDs/cluster17cellIDs.txt", col.names = "clust17")
clust17.cells <- sapply(clust17.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust10.cells <- read.table(file = "../Seuratv1_clusterCellIDs/cluster10cellIDs.txt", col.names = "clust10")
clust10.cells <- sapply(clust10.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
clust11.cells <- read.table(file = "../Seuratv1_clusterCellIDs/cluster11cellIDs.txt", col.names = "clust11")
clust11.cells <- sapply(clust11.cells, function(x) paste0(gsub("CMP", "CMPm2", x), "-1"))
```

@@

## Identify variable genes for new biomark
```{r}
length(cmp.object@assays$RNA@var.features)
```
```{r}
top100.var <- cmp.object@assays$RNA@var.features[1:100]
length(top100.var)
```

@@

### Clustree
what's the max resolution we can achieve while keepign clusters stable?
```{r fig.width = 10, fig.height = 5}
clustree(cmp.object, prefix = "RNA_snn_res.", node_colour = "sc3_stability", exprs = "scale.data") + 
    scale_color_continuous(low = 'red3', high = 'white')
```
I think I'm liking res.1.0 from this

@@

Create `FindAllMarkers()` lists for GSEA
```{r }
Idents(cmp.object) <- "RNA_snn_res.2.5"
res.2.5.allmarkers <- FindAllMarkers(cmp.object)
```

## Map HGNC symbols
```{r}
Mouse2HumanTable <- Mouse2Human(res.2.5.allmarkers$gene)

@@

calculate `FindMarkers()` that distinguish each cluster (might overlab between clusters)
```{r}
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1", "RNA_snn_res.1.5", "RNA_snn_res.2", "RNA_snn_res.2.5", "clust.ID")
for(tested.ident in ident.list){
	object.copy <- cmp.object
	Idents(object.copy) <- tested.ident
	print(paste("testing", tested.ident))
	for (cluster in sort(as.numeric(levels(object.copy@meta.data[[tested.ident]])))){
		print(paste("looking at cluster", cluster))
		cluster.markers <- FindMarkers(object.copy, ident.1 = cluster)
		try(
			xlsx::write.xlsx(x = cluster.markers[,c("avg_log2FC", "p_val_adj")], 
											 file = paste0(projectName, "_FindMarkers_", gsub("RNA_snn_", "", tested.ident), ".xlsx"), 
											 sheetName = paste0("clst", cluster), 
											 col.names = TRUE, 
											 row.names = TRUE, 
											 append = TRUE)
		)	
	}
	remove(object.copy)
}
```

@@

# Compare @g hierarchcial clusteirng
